Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2014-12-05 draft_lm1.tex
minor fixes in the bibtex

Figure \ref{Fig:S0}, shows the model from (\ref{eq:model}) fitted to the data. 
In it we can see that the susceptibles series in each epidemic starts at the 
estimated level of $S_0$. The proportion of susceptibles may seem low, but we 
must remember that these estimates are being affected by an unknown 
underreporting factor, which experts suggest is somewhere between 5 and 10, 
i.e. for every case observed there are 5 or 10 unobserved. Since this 
underreporting ration affects both the numerator and denominator of 
(\ref{eq:AR}), its effects should cancel out, giving us an unbiased attack ratio 
estimate. One other possible source of bias which would lead to the 
underestimation of $S_0$ could come from a significant part of the population 
not being exposed to the disease. But, as we can see in figure xx\todo{add 
figure with the four maps}, the disease spread pretty much homogeneously over 
the entire city (in the last four epidemics, at least).

>>>>

Figure \ref{Fig:S0}, shows the model from (\ref{eq:model}) fitted to the data. 
In it we can see that the susceptibles series in each epidemic starts at the 
estimated level of $S_0$. The proportion of susceptibles may seem low, but we 
must remember that these estimates are being affected by an unknown 
underreporting factor, which experts suggest is somewhere between 5 and 10, 
i.e. for every case observed there are 5 or 10 unobserved. Since this 
underreporting ration affects both the numerator and denominator of 
(\ref{eq:AR}), its effects should cancel out, giving us an unbiased attack ratio 
estimate. One other possible source of bias which would lead to the 
underestimation of $S_0$ could come from a significant part of the population 
not being exposed to the disease. But, as we can see in figure xx\todo{add 
figure with the four maps}, the disease spreads pretty much homogeneously over 
the entire city (in the last four epidemics, at least).
